The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2018-05-31 Paper/jaccardbaetica.tex
add magu

The approach proposed here is based on the idea of measuring the similarity between amphora workshops by quantifying similar stamps. A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index \citep{morisita_measuring_1959, horn_measurement_1966}. This method was performed to measure the overlap between different samples of sets. Generally, it describes the dissimilarity between the system of two communities based on the idea of inverse correlation between diversity and species (CITAR AQUI MANGURRIAN)

>>>>

The approach proposed here is based on the idea of measuring the similarity between amphora workshops by quantifying similar stamps. A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index \citep{morisita_measuring_1959, horn_measurement_1966}. This method was performed to measure the overlap between different samples of sets. Generally, it describes the dissimilarity between the system of two communities based on the idea of inverse correlation between diversity and species \citep{magurran_why_1988}.
